---
title: "Data Analysis Report on Police Misconduct"
author: "Bright Hoang | Paul Oh | Salma Yusuf"
output: html_document
date: "Autumn 2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

``` {r summary_info_code, echo = FALSE, include = FALSE}
source("../source/summary_info.R")
source("../source/chart_1.R")
source("../source/chart_2.R")
```

## This will be the start of my example:

```{r summary_info_plot, echo = FALSE}
bh_plot
```

### My number is `r num` and im  not a `r word`

The FitnessGram^TM^ Pacer Test is a multistage aerobic capacity test that progressively gets more difficult as it continues. The 20 meter pacer test will begin in 30 seconds. Line up at the start. The running speed starts slowly, but gets faster each minute after you hear this signal. [beep] A single lap should be completed each time you hear this sound. [ding] Remember to run in a straight line, and run as long as possible. The second time you fail to complete a lap before the sound, your test is over. The test will begin on the word start. On your mark, get ready, start.


## Chicago Test Dynamic Paragraph

There were a total of `r round(chicago_info$total)` dollars spent on police settlements.

**Chicago Summary Points:**

Police misconduct cases involving `r chicago_highest_median_type` had the 
highest median settlements of $`r chicago_highest_median`.

The city of Chicago spent a median of $`r chicago_yearly_median` annually on
police misconduct settlements.

The city of Los Angeles spent a total amount of $`r total_settlements` on police settlements in 2018.

## Charts:

### Salma: 

```{r echo = FALSE}
LA_set_year
```





### Bright: 
```{r echo = FALSE}
chichart
```

This is a stacked bar chart that visualizes the proportion of settlement money spent on different *types* of police misconduct in Chicago. This is important to observe because we can see which category of misconduct has the highest consequences and settlement amount. We can observe that **reversed conviction** and **serious excessive force** cases pay the highest amount of settlements.