---
title: "Data Analysis Report on Police Misconduct"
author: "Bright Hoang | Paul Oh | Salma Yusuf"
output: html_document
date: "Autumn 2022"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

```{r summary_info_code, echo = FALSE, include = FALSE}
source("../source/summary_info.R")
source("../source/chart_1.R")
source("../source/chart_2.R")
```

## This will be the start of my example:

```{r summary_info_plot, echo = FALSE}
bh_plot
```

### My number is `r num` and im not a `r word`

The FitnessGram^TM^ Pacer Test is a multistage aerobic capacity test that progressively gets more difficult as it continues. The 20 meter pacer test will begin in 30 seconds. Line up at the start. The running speed starts slowly, but gets faster each minute after you hear this signal. [beep] A single lap should be completed each time you hear this sound. [ding] Remember to run in a straight line, and run as long as possible. The second time you fail to complete a lap before the sound, your test is over. The test will begin on the word start. On your mark, get ready, start.

## Chicago Test Dynamic Paragraph

There were a total of `r round(chicago_info$total)` dollars spent on police settlements.

**Chicago Summary Points:**

Police misconduct cases involving `r chicago_highest_median_type` had the highest median settlements of \$`r chicago_highest_median`.

The city of Chicago spent a median of \$`r chicago_yearly_median` annually on police misconduct settlements.

The city of Los Angeles spent a total amount of \$`r total_settlements` on police settlements in 2018.

## Charts:

### Salma:

```{r echo = FALSE}
LA_set_year
```

This is a column chart representing the amount of *settlement* money spent each *year*. The x-axis shows each year included in the data set, and the y-axis shows the total amount of settlements the city of Los Angeles spent each year. I chose to make this chart to show how much money was spent each year due to police misconduct. We can see that there is a significant amount that was spent in 2016 compared to the other years, and 2013 had the least amount of money spent.

### Bright:

```{r echo = FALSE}
chichart
```

This is a stacked bar chart that visualizes the proportion of settlement money spent on different *types* of police misconduct in Chicago. This is important to observe because we can see which category of misconduct has the highest consequences and settlement amount. We can observe that **reversed conviction** and **serious excessive force** cases pay the highest amount of settlements.

### Paul:

```{r echo = FALSE}
baltimore_boxplot
```

This is a box plot showing the **spread** of settlement money throughout different categories of cases within the city of Baltimore, Maryland. Within the summary_allegations axis are the different labels for the categories of cases, which go from Gun Trace Task Force officer misconducts, violations of civil rights, false arrests, false imprisonments, illegal searches, malicious prosecutions, and uses of force in order from left to right. The amount_awarded axis shows the settlement money used. Although there are two outliers within the violation of civil rights category, both of which exceed $600,000 and have been excluded from this box plot, this visualization shows that there is a much *greater spread of settlement money* going into the GTTF officer misconduct cases than the other cases. From this, we can figure out which cases produce a ***greater issue*** in police misconduct cases.